---
title: "Stats506 Final Project Report"
author: "Yan Chen, yanchann@umich.edu"
date: "`r format.Date(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE, message=FALSE}
# 79: -----------------------------------------------------------------------
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
results = read_csv('results/cbecs.csv')
```

## **Introduction**

Energy conservation is a hot issue nowadays. Energy can be conserved by reducing
wastage and losses, improving efficiency through technological upgrades and
improved operation and maintenance. In this project, I am working on the
problem:

**Do buildings with electrical upgrades in the past year consume less electricity than those without recent upgrades?**


## **Data / Methods**

I use the data from the 2012 US Commercial Building Energy Consumption Survey 
[(CBECS)](https://www.eia.gov/consumption/commercial/data/2012) 

I will calculate the estimated mean building-level energy
intensity of the electricity (`bleu`) which is defined as 
**annual electricity consumption (`ELCNS`) / square foot (`SQFT`)** 
for buildings with recent electrical upgrades (`RENELC`) and those without.
The results are further stratified by the primary building activity (`PBA`) and
geography (`REGION`).

I focus on five major building activity: office, warehouse, education,
shopping, and service when doing the analysis since these five categories have
more observations than others.

The first thing to do is to clean the data: select the observations in the five 
categories and remove rows with any missing value. Secondly, I use the statement
`PROC SURVEYMEANS` to calculate the estimated mean energy intensity of 
electricity and calculate the 95% confidence intervals using the replicate
weights (`FINALWT1-197`).

The source code can be accessed at my 
[Github repo](https://github.com/yanchannn/Stats506_FinalProject).

## **Results** {.tabset .tabset-pills}
### Figure
```{r plot, echo = FALSE, fig.cap=cap1}
cap1 = paste0(
  "**Figure 1.** *Energy intensity of electricity* ", 
  "This figure shows estimated mean energy intensity of electricity in 2012."
)
results %>%
  mutate(
    `Primary Building Activity` = activity,
    `Electrical Upgrade` = RENELC
  ) %>%
  ggplot( aes(y = Mean, x = REGION, color = `Electrical Upgrade`) ) +
  geom_point( position = position_dodge(width = .5), alpha = 0.5, size = 1) +
  geom_errorbar( 
    aes(ymin = LowerCLMean, ymax = UpperCLMean), 
    alpha = 0.5, 
    position = position_dodge(width = .5)
  ) + 
  coord_flip() +
  facet_wrap(~ `Primary Building Activity`) + 
  theme_bw() +
  scale_color_manual(values = c('darkblue', 'darkred')) + 
  ylab( "Mean energy intensity of electricity in 2012" ) +
  xlab('Region')
```

### Table
```{r table, echo = FALSE}
cap2 = paste0("**Table 1.** *Energy intensity of Electricity in 2012*",
              "Numbers in parantheses represent 95% confidence intervals.")

res = results %>%
  transmute( 
    `Region` = REGION, 
    `Primary Building Activity` = activity,
    `Electrical Upgrade` = RENELC,
    `Mean energy intensity` = 
      sprintf('<div>%4.2f</div> <div>(%4.2f, %4.2f)</div>',
                     Mean, LowerCLMean,UpperCLMean)
  ) 

tab1 = res %>% 
  filter(`Electrical Upgrade` == 'Yes')

tab2 = res %>% 
  filter(`Electrical Upgrade` == 'No')

tab3 = left_join(tab1, tab2, by = c('Region', 'Primary Building Activity'))


tab3 %>% select(
  Region, `Primary Building Activity`, 
  `Yes` = `Mean energy intensity.x`,
  `No` = `Mean energy intensity.y`
) %>%
  knitr::kable(
    format = 'html', 
    escape = FALSE, 
    align = 'llcc',
    cap = cap2
  ) %>%
  kableExtra::kable_styling("striped", full_width = TRUE) %>%
  kableExtra::add_header_above(header = c(' ' = 2, 'Electrical Upgrade' = 2))

```


## **To-do**

- add conclusion and comments for the results

- improve the figure and table format

- add inline comments to the code

- perform t-test of the results and add p-values to the table
