---
title: "Stats506 Final Project Report"
author: "Yan Chen, yanchann@umich.edu"
date: "`r format.Date(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    code_folding: hide
    theme: united
---

```{r setup, include=FALSE, message=FALSE}
# 79: -----------------------------------------------------------------------
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
results = read_csv('results/cbecs.csv')
diffmean = read_csv('results/diffmean.csv')
```

## **Introduction**

Energy conservation is a hot issue nowadays. Energy can be conserved by 
reducing wastage and losses, improving efficiency through technological 
upgrades and improved operation and maintenance. In this project, 
I am working on the problem:

**Do buildings with electrical upgrades in the past year consume less electricity than those without recent upgrades?**

I conducted a preliminary analysis on the 2012 CBECS data trying to find 
whether there are significant differences in building-level energy intensity 
of the electricity for buildings with and without electrical upgrade.

## **Data / Methods**

I use the data from the 2012 US Commercial Building Energy Consumption Survey 
[(CBECS)](https://www.eia.gov/consumption/commercial/data/2012) 

I calculate the estimated mean building-level energy
intensity of the electricity (`bleu`) which is defined as 
**annual electricity consumption (`ELCNS`) / square foot (`SQFT`)** 
for buildings with recent electrical upgrades (`RENELC`) and those without.
The results are stratified by the primary building activity (`PBA`) and
geography (`REGION`).

Here I focus on five major building activities: office, warehouse, education,
shopping, and service since these five categories have more observations than
others.

The first thing to do is to clean the data: select the observations in the five
categories and remove rows with any missing value. 

Secondly, I use the statement
`PROC SURVEYMEANS` to calculate the estimated mean energy intensity of 
electricity and calculate the 95% confidence intervals using the replicate
weights (`FINALWT1-197`) as described in the 
[documentation](https://www.eia.gov/consumption/commercial/data/2012/pdf/user_guide_public_use_aug2016.pdf)

Thirdly, I calculate the differences(upgrade less not upgrade) 
and the corresponding 95% CIs where I assume the estimates are independent. 

Finally, I use `diffmeans` to perform t-tests on the estimated mean energy
intensity of electricity and get the p-values.

The source code can be accessed at my 
[Github repo](https://github.com/yanchannn/Stats506_FinalProject).

## **Results** {.tabset .tabset-pills}
### Figure
```{r plot, fig.cap=cap1, fig.width=10, fig.height=7}
cap1 = paste0(
  "**Figure 1.** *Energy intensity of electricity* ", 
  "This figure shows estimated mean energy intensity of electricity in 2012."
)
results %>%
  mutate(
    `Primary Building Activity` = activity,
    `Electrical Upgrade` = RENELC
  ) %>%
  ggplot( aes(y = Mean, x = REGION, color = `Electrical Upgrade`) ) +
  geom_point( position = position_dodge(width = .5), alpha = 0.5, size = 1) +
  geom_errorbar( 
    aes(ymin = LowerCLMean, ymax = UpperCLMean), 
    position = position_dodge(width = .5),
    width = .2
  ) + 
  coord_flip() +
  facet_wrap(~ `Primary Building Activity`) + 
  theme_bw() +
  scale_color_manual(values = c('darkblue', 'darkred')) + 
  ylab( "Mean energy intensity of electricity in 2012" ) +
  xlab('Region')
```

### Table
```{r table}
cap2 = paste0("**Table 1.** *Energy intensity of Electricity in 2012* ",
              "Numbers in parantheses represent 95% confidence intervals.")

res = results %>%
  transmute( 
    `Region` = REGION, 
    `Primary Building Activity` = activity,
    `Electrical Upgrade` = RENELC,
    `Mean energy intensity` = 
      sprintf('<div>%4.2f</div> <div>(%4.2f, %4.2f)</div>',
                     Mean, LowerCLMean,UpperCLMean),
    `se` = StdErr,
    `lwr` = LowerCLMean,
    `upr` = UpperCLMean,
    `est` = Mean
  ) 

tab1 = res %>% 
  filter(`Electrical Upgrade` == 'Yes')

tab2 = res %>% 
  filter(`Electrical Upgrade` == 'No')

diff = tab1 %>%
  left_join(
    tab2, by = c("Region", "Primary Building Activity")
    ) %>%
  transmute(
    Region, `Primary Building Activity`,
    diff = est.x - est.y,
    se = sqrt(se.x + se.y),
    lwr = diff - 1.96 * se,
    upr = diff + 1.96 * se,
    difference = sprintf('<div>%4.2f</div> <div>(%4.2f, %4.2f)</div>',
                     diff, lwr, upr),
    ) 

tab3 = left_join(
  select(tab1, c(1, 2, 4)), 
  select(tab2, c(1, 2, 4)), 
  by = c('Region', 'Primary Building Activity')) %>%
  left_join(
    select(diff, c(1, 2, 7)), by = c('Region', 'Primary Building Activity'))

tab4 = diffmean %>% 
  filter(`activity` == `_activity`& `REGION` == `_REGION`) %>%
  transmute(
    `Region` = REGION, 
    `Primary Building Activity` = activity,
    `p-value` = Probt
  )
  
tab3 %>% 
  left_join(tab4, by = c('Region', 'Primary Building Activity')) %>%
  select(
    Region, `Primary Building Activity`, 
    `Yes` = `Mean energy intensity.x`,
    `No` = `Mean energy intensity.y`,
    `Diff` = difference,
    `p-value`) %>%
  knitr::kable(
    format = 'html', 
    escape = FALSE, 
    align = 'llcccc',
    cap = cap2
  ) %>%
  kableExtra::kable_styling("striped", full_width = TRUE) %>%
  kableExtra::add_header_above(
  header = c(' ' = 2, 'Electrical Upgrade' = 2, ' ' = 2))

```

From Figure 1 and Table 1 we can see that there are not many differences in
the results between buildings with upgrades in the last year and those without upgrades. Only Office buildings have a significant drop after electrical
upgrades at 0.05 significance level. 

We can also notice that the 95% CIs for buildings with upgrades are much wider. 


## **Conclusion**

- There is no evident drops in electricity consumption after recent 
electrical upgrades.

The answer to the question depends on the principle building activity: 

- Buildings with principle activity as office in all the four regions 
consume less after the upgrades.

- Buildings with principle activity as education and shopping actually 
consume more after the upgrades.

### Limitation

- There might be other confounders that will affect the electricity consumption
for example, whether electricity is the main source of energy or the building 
depends more on other energy. 

- The number of observations is too small for each group, leading to
large variances. Thus, it is hard to get a general answer to the question. 

